A novel method for detecting coalescing binaries in near realtime with Advanced LIGO and beyond \editorial{Submit to PRD or CQG?}

### 2011-02-18 results.tex
Added description of noninjections
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@646 ccdd05d5-56c1-461a-bf98-85f6876523b4
removed some outline stuff that has been converted to prose
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@648 ccdd05d5-56c1-461a-bf98-85f6876523b4

\begin{itemize}
\item 1 day of simulated $h(t)$.
\item $h(t)$ has power spectrum \sout{prescribed for ``zero detuning, high power'' model in \cite{Shoemaker:2009p9770}} that somewhat resembles initial \textsc{ligo} noise models
\item $h(t)$ generated by passing white, Gaussian noise through a bank of \textsc{iir} filters
\item 1 noninjections run
\item 10 injections runs
\item injections are distributed uniformly in log distance, uniformly in sky location and binary orientation
\item injections are reweighted to be uniformly distributed in volume
\item injections are 80$\pm$20 seconds apart
\item there are $\approx$ 10k injections
\end{itemize}

>>>>

\subsection{Noninjection population}

We completed one injection-free pass over the 14~day dataset. \editorial{And **why**?  This part is too terse.}

\subsection{Trigger reduction procedure}

{\color{red} Describe triggering, clustering, injection finding, injection re-weighting, and \textsc{roc} plotting here.}
